Using Mean-Squared-Error in Log-Transformed Domain to Evaluate Speckle Filters.

### 2012-07-09 article.tex
some comment for your changes

\begin{figure}[h]
\centering
%\centerline{
\begin{tabular}{c}
	\subfloat[amplitude]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/amplitude_hist_model_pdf_scene1.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[intensity]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/intensity_hist_model_pdf_scene1.eps} 	
		 \label{intensity}
	} \\
	\subfloat[log amplitude]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/log_amplitude_histogram.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[log intensity]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/log_intensity_histogram.eps} 	
		 \label{intensity}
	} 
\end{tabular}
%}
\caption{Observed histogram in homogenous area and modelled pdf response}
\label{fig:modelled_response}
\end{figure}

@@

In this section, the methodology to evaluate speckle filters on homogeneous area in log-transformed domain is illustrated.
Under the condition of homogeneity, speckle filters are supposed to estimate with negligible bias.
Then the filters are traditionally compared by measuring its speckle suppression power using the ENL index.
Consequently in the log-transformed domain, the first component of MSE evaluation (i.e. bias evaluation) is probably insignificant in comparison to the other component, namely, variance evaluation. 
The following subsection gives theoretical justification for our methodology where variance evaluation is shown to be mathematically related to the ENL index.
The last subsection details how variance evaluation in log-transformed domain can be employed to evaluate the levels of speckle in homogeneous area.

@@

Before we begin, Fig. \ref{fig:simul_process_filter_schema} illustrates the general schema of the various experiments presented in this paper.
The ``SAR Processor'' block indicates either 
	the normal process of SAR processing where the unknown ground radiometric attribute ($X$) is captured in $\tilde{X}$ or
	the simulation process where the noisy SAR data $\tilde{X}$ is simulated from a known ground-truth pattern $X$.
In this paper, fully developed speckle assumption is employed, which allow for easier simulation process.	
Eventhough different levels of noise can be simulated, in the experiments presented here, only single-look are simulated, and the similar boxcar filter is studied.

@@

\subsection{ Estimating ENL from MSE index in homogeneous areas }

@@

%Next we will be showing that the ENL, i.e. L, can be estimated from a given $var(Y^L)$. 
Taking results of the Euler proof for the Basel problem, we have $\frac{\pi^2}{6} = \sum^{\infty}_{i=1}{ \frac{1}{i^2} } $, then $var(Y^L)= \frac{1}{\ln^2(2)} \left( \sum^{\infty}_{i=L}{ \frac{1}{i^2} } \right) $.
Noting that $ \frac{1}{i} - \frac{1}{i+1} = \frac{1}{i(i+1)} < \frac{1}{i^2} < \frac{1}{i(i-1)} = \frac{1}{i-1} - \frac{1}{i}$, then $ \frac{1}{L} - \frac{1}{\infty} < \sum^{\infty}_{i=L}{ \frac{1}{i^2} }  < \frac{1}{L-1} - \frac{1}{\infty} $.
In fact, we could estimate:
\begin{equation}
  var(\hat{X}^L) = \frac{1}{(L-0.5) \ln^2(2) }
\label{eqn:perf_index_analytic}
\end{equation}
Thus, the Equivalent Number of Look, i.e. L, can be estimated as:
\begin{equation}
L = \frac{1}{var(\hat{X}^L) \ln^2(2)} + 0.5
\label{eqn:enl_analytic}
\end{equation}

@@

\begin{table}
\centering
\begin{tabular}{r|c|c|c|r}
ENL & Var (Theory) & Var (Analysis) & Var (Observed) & ENL (Estimated) \\
\hline
2  & 1.3423 & 1.3876 & 1.3452 (0.0031) & 2.047 (0.0036)\\
3  & 0.8221 & 0.8326 & 0.8191 (4.2e-5) & 3.041 (0.0001)\\
4  & 0.5907 & 0.5947 & 0.5941 (0.0059) & 4.004 (0.0351)\\
5  & 0.4607 & 0.4625 & 0.4622 (0.0010) & 5.003 (0.0099)\\
6  & 0.3774 & 0.3784 & 0.3800 (0.0009) & 5.977 (0.0131)\\
7  & 0.3196 & 0.3202 & 0.3188 (0.0037) & 7.029 (0.0769)\\
8  & 0.2771 & 0.2775 & 0.2786 (0.0002) & 7.970 (0.0065)\\
9  & 0.2446 & 0.2449 & 0.2455 (0.0007) & 8.979 (0.0244)\\
10 & 0.2189 & 0.2191 & 0.2183 (0.0012) & 10.035 (0.0538)\\
11 & 0.1981 & 0.1982 & 0.1975 (0.0001) & 11.038 (0.0063)\\
12 & 0.1809 & 0.1809 & 0.1810 (0.0022) & 12.001 (0.1419)\\
13 & 0.1664 & 0.1665 & 0.1661 (0.0002) & 13.031 (0.0191)\\
14 & 0.1541 & 0.1542 & 0.1534 (0.0016) & 14.068 (0.1387)\\
15 & 0.1435 & 0.1435 & 0.1432 (0.0019) & 15.036 (0.1967)\\
16 & 0.1342 & 0.1343 & 0.1342 (0.0009) & 16.006 (0.0987)\\
17 & 0.1261 & 0.1261 & 0.1249 (0.0005) & 17.159 (0.0636)\\
18 & 0.1189 & 0.1189 & 0.1192 (0.0010) & 17.959 (0.1406)\\
19 & 0.1125 & 0.1125 & 0.1126 (0.0004) & 18.976 (0.0788)\\
20 & 0.1067 & 0.1067 & 0.1074 (0.0005) & 19.889 (0.0937)\\
21 & 0.1015 & 0.1015 & 0.1017 (0.0002) & 20.975 (0.0357)\\
22 & 0.0968 & 0.0968 & 0.0970 (0.0002) & 21.952 (0.0337)\\
23 & 0.0925 & 0.0925 & 0.0924 (0.0006) & 23.027 (0.1386)\\
24 & 0.0886 & 0.0886 & 0.0887 (0.0002) & 23.957 (0.0507)\\
25 & 0.0849 & 0.0849 & 0.0846 (0.0007) & 25.094 (0.1934)
\end{tabular}
\caption{ Speckle Suppression Power: ENL and Variance }
\label{tab:enl_in_log_domain}
\end{table}

@@

\begin{table}
\centering
\begin{tabular}{c|r|c|c|r}
Pattern  & Filter  & AUC & MSE (true)   & MSE (noise)      \\% &85\%             &90\%\\
\hline
 point  &  unfiltered  &  0.741 (0.7e-3)  &  4.101 (1.3e-3)  &  2e-33 (4e-36) \\
 point  &  pde  &  0.789 (1.3e-3)  &  1.291 (5.1e-3)  &  1.817 (2.2e-3)\\
 point  &  map  &  0.813 (1.4e-3)  &  1.679 (2.2e-3)  &  2.183 (7.4e-3)\\
 point  &  frost  &  0.836 (1.8e-3)  &  0.536 (2.4e-3)  &  4.976 (6.9e-3)\\
 point  &  lee  &  0.857 (0.9e-3)  &  0.615 (3.1e-3)  &  3.189 (0.9e-3)\\
 point  &  boxcar  &  0.871 (1.5e-3)  &  0.471 (1.7e-3)  &  4.503 (5.4e-3)\\
 point  &  kuan  &  0.882 (1.1e-3)  &  0.448 (2.3e-3)  &  3.859 (3.4e-3)\\
\hline
 edge  &  unfiltered  &  0.738 (1.5e-4)  &  4.128 (9.0e-3)  &  2e-33 (1e-35)\\
 edge  &  pde  &  0.783 (0.6e-4)  &  1.409 (0.3e-3)  &  1.589 (0.4e-2)\\
 edge  &  map  &  0.830 (0.6e-4)  &  1.712 (3.5e-3)  &  2.184 (0.8e-2)\\
 edge  &  frost  &  0.841 (0.6e-4)  &  0.551 (0.1e-3)  &  5.035 (1.3e-2)\\
 edge  &  boxcar  &  0.871 (0.2e-4)  &  0.486 (0.2e-3)  &  4.560 (1.3e-2)\\
 edge  &  lee  &  0.872 (0.7e-4)  &  0.619 (2.2e-3)  &  3.233 (1.3e-2)\\
 edge  &  kuan  &  0.885 (0.4e-4)  &  0.471 (2.0e-3)  &  3.909 (1.1e-2)\\
\hline
 checker  &  unfiltered  &  0.738 (4.5e-4)  &  4.11 (7.8e-3)  &  2e-33 (5e-36)\\
 checker  &  pde  &  0.785 (6.2e-4)  &  1.445 (2.6e-3)  &  1.586 (2.4e-3)\\
 checker  &  map  &  0.836 (4.0e-4)  &  1.663 (1.1e-3)  &  2.213 (4.6e-3)\\
 checker  &  frost  &  0.855 (5.6e-4)  &  0.528 (2.2e-3)  &  4.965 (9.3e-3)\\
 checker  &  lee  &  0.879 (2.2e-4)  &  0.605 (1.7e-3)  &  3.229 (2.8e-3)\\
 checker  &  boxcar  &  0.883 (6.4e-4)  &  0.466 (2.4e-3)  &  4.493 (9.1e-3)\\
 checker  &  kuan  &  0.894 (4.2e-4)  &  0.453 (0.9e-3)  &  3.860 (9.5e-3)\\
\hline
 line  &  unfiltered  &  0.737 (1.1e-3)  &  4.129 (7.3e-3)  &  2e-33 (6e-36)\\
 line  &  pde  &  0.752 (1.2e-3)  &  1.339 (2.0e-3)  &  1.885 (3.7e-3)\\
 line  &  map  &  0.801 (1.6e-3)  &  1.706 (5.8e-3)  &  2.188 (3.5e-3)\\
 line  &  frost  &  0.831 (1.3e-3)  &  0.551 (1.1e-3)  &  5.023 (0.5e-3)\\
 line  &  lee  &  0.847 (1.5e-3)  &  0.623 (2.9e-3)  &  3.228 (4.8e-3)\\
 line  &  boxcar  &  0.865 (1.3e-3)  &  0.486 (0.9e-3)  &  4.549 (0.9e-3)\\
 line  &  kuan  &  0.874 (1.9e-3)  &  0.464 (1.9e-3)  &  3.897 (4.9e-3)\\
\hline

@@

\begin{table}
\centering
\begin{tabular}{c|r|c|c|r}
Pattern  & AUC - true MSE (p-value) & AUC - benchmark MSE (p-value) \\
\hline
edge & -0.8958 (1.5e-05) &   -0.9778  (1.6e-09) \\
point &     -0.9012   (1.1e-05)   &    -0.9816        (5.3e-10) \\
checker &   -0.9077     (7.3e-06)  &  -0.9829       (3.5e-10) \\
line &      -0.8223     (3.1e-04)  &   -0.9421       (4.8e-07) \\
\hline
\end{tabular}

@@

\begin{figure}
\begin{tabular}{c}
	\subfloat[A Rural Area in Vietnam]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/P1090360.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[A Suburb of Ha Noi]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/P1090253.eps} 	
		 \label{intensity}
	} %\\
%	\subfloat[NTU Campus]{
%		 \epsfxsize=1.5in
%		 \epsfysize=1.5in
%		 \epsffile{src/Aerialcampus.eps} 	
%		 \label{amplitude}
%	} 
%	\hfill	
%	\subfloat[Chu Thap Island of Vietnam]{
%		 \epsfxsize=1.5in
%		 \epsfysize=1.5in
%		 \epsffile{src/fiery.eps} 	
%		 \label{intensity}
%	} 
\end{tabular}
\caption{Ground Truth Images for simulation}
\label{fig:real_simulated_images}
\end{figure}

@@

\begin{table}
\centering
\begin{tabular}{r|r|c|c}
Pattern  & Filter  & MSE (true)   & MSE (noise)      \\% &85\%             &90\%\\
%\hline
%chu thap island	& none		& 4.1066	& 1.2e-33\\
%chu thap island	& pde			& 1.7966	& 1.0866\\
%chu thap island	& lee			& 0.5772	& 3.2378\\
%chu thap island	& frost		& 0.4701	& 4.8608\\
%chu thap island	& kuan		& 0.4196	& 3.7945\\
%chu thap island	& boxcar	& 0.4165	& 4.3952\\
%\hline
%ntu campus	& none		& 4.1231	& 8.7e-35\\
%ntu campus	& pde			& 3.6598	& 0.0733\\
%ntu campus	& lee			& 0.6335	& 3.2673\\
%ntu campus	& frost		& 0.5776	& 5.0569\\
%ntu campus	& boxcar	& 0.5136	& 4.5839\\
%ntu campus	& kuan		& 0.4910	& 3.9444\\
\hline
vietnam rural	& none		& 4.1174	& 3.9e-35\\
vietnam rural	& pde			& 3.8022	& 0.0368\\
vietnam rural	& lee			& 0.4984	& 3.2555\\
vietnam rural	& frost		& 0.3490	& 4.6856\\
vietnam rural	& kuan		& 0.3396	& 3.6877\\
vietnam rural	& boxcar	& 0.3107	& 4.2328\\
\hline
hanoi suburb	& none		& 4.1321	& 4.1e-35\\
hanoi suburb	& pde			& 3.8004	& 0.0391\\
hanoi suburb	& lee			& 0.5261	& 3.2598\\
hanoi suburb	& frost		& 0.3811	& 4.7427\\
hanoi suburb	& kuan		& 0.3619	& 3.7270\\
hanoi suburb	& boxcar	& 0.3395	& 4.2882\\
\hline
\end{tabular}

@@

%\begin{figure*}
\begin{figure}
\normalsize
\begin{center}
\begin{tabular}{c}
	\subfloat[Simulated GrayScale Image (ground-truth)]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/simulated_images.vietnam_rural.gt.jpg.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Unfiltered Noisy Image (true MSE = 4.1174)]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/simulated_images.vietnam_rural.none.fi.jpg.eps} 	
		 \label{intensity}
	} \\
	\subfloat[PDE Result (true MSE = 3.8022, residual MSE = 0.0073)]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/simulated_images.vietnam_rural.pde.fi.jpg.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Lee Result (true MSE = 0.4984, residual MSE = 3.25553)]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/simulated_images.vietnam_rural.lee.fi.jpg.eps} 	
		 \label{intensity}
	} \\
	\subfloat[Frost Result (true MSE = 0.3490, residual MSE = 4.6856)]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/simulated_images.vietnam_rural.frost.fi.jpg.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Boxcar Result (true MSE = 0.3107, residual MSE = 4.2328)]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/simulated_images.vietnam_rural.boxcar.fi.jpg.eps} 	
		 \label{intensity}
	}
\end{tabular}

@@

\begin{table}
\centering
\begin{tabular}{c|r}
filter & MSE (noise)\\
\hline
pde & 0.2583\\
map & 2.6936\\
kuan & 3.3924\\
lee & 3.4172\\
boxcar & 3.6918\\
frost & 4.1191\\
\hline
SLC unfiltered MSE & 4.1167  
\end{tabular}
\caption{Our Conjecture: Most Suitable Speckle Filter For The Scene Can Be Chosen Using The Residual MSE.}
\label{tab:mse_in_real_image}
\end{table}

%\begin{figure*}
\begin{figure}
\normalsize
\begin{center}
\begin{tabular}{c}
	\subfloat[PDE Filter: MSE (noise) = 0.2583]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_real.log.image.pde.jpg.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[MAP Filter: MSE (noise) = 2.6936]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_real.log.image.map.jpg.eps} 	
		 \label{intensity}
	} \\
	\subfloat[Lee Filter: MSE (noise) = 3.4172]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_real.log.image.lee.jpg.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Frost Filter: MSE (noise) = 4.1191]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_real.log.image.frost.jpg.eps} 	
		 \label{intensity}
	}
\end{tabular}

\caption{Filtering Real Images: Visual Validation}
\label{fig:real_image_results}
\end{center}
\end{figure}
%\end{figure*}

>>>>

\begin{figure}[h]
\centering
%\centerline{
\begin{tabular}{c}
	\subfloat[amplitude]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/amplitude_histogram.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[intensity]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/intensity_histogram.eps} 	
		 \label{intensity}
	} \\
	\subfloat[log amplitude]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/log_amplitude_histogram.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[log intensity]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/log_intensity_histogram.eps} 	
		 \label{intensity}
	} 
\end{tabular}
%}
\caption{Observed histogram in homogenous area and modelled pdf response}
\label{fig:modelled_response}
\end{figure}

@@

In this section, the methodology to evaluate speckle filters on homogeneous area in log-transformed domain is illustrated.
Under the condition of homogeneity, speckle filters are supposed to estimate with negligible bias.
Then the filters are traditionally compared by measuring its speckle suppression power using the ENL index.
Consequently in the log-transformed domain, the first component of MSE evaluation (i.e. bias evaluation) is probably insignificant in comparison to the other component, namely, variance evaluation. 
Subsection \ref{sec:homogeneous_theoretical} gives theoretical justification for our methodology where variance evaluation is shown to be mathematically related to the ENL index.
The last subsection details how variance evaluation in log-transformed domain can be employed to evaluate the levels of speckle in homogeneous area.
But before we begin, a brief schematic overview description of our evaluational methodology is presented.

@@

Fig. \ref{fig:simul_process_filter_schema} illustrates the general schema of the various experiments presented in this paper.
The ``SAR Processor'' block indicates either 
	the normal process of SAR processing where the unknown ground radiometric attribute ($X$) is captured in $\tilde{X}$ or
	the simulation process where the noisy SAR data $\tilde{X}$ is simulated from a known ground-truth pattern $X$.
In this paper, fully developed speckle assumption is employed, which allow for easier simulation process.	
Eventhough different levels of noise can be simulated, in the experiments presented here, only single-look are simulated, and the similar boxcar filter is studied.

@@

\subsection{ Estimating ENL from MSE index in homogeneous areas }
\label{sec:homogeneous_theoretical}

@@

%Next we will be showing that the ENL, i.e. L, can be estimated from a given $var(Y^L)$. 
Taking results of the Euler proof for the Basel problem, we have $\frac{\pi^2}{6} = \sum^{\infty}_{i=1}{ \frac{1}{i^2} } $, then $var(Y^L)= \frac{1}{\ln^2(2)} \left( \sum^{\infty}_{i=L}{ \frac{1}{i^2} } \right) $.
Noting that $ \frac{1}{i} - \frac{1}{i+1} = \frac{1}{i(i+1)} < \frac{1}{i^2} < \frac{1}{i(i-1)} = \frac{1}{i-1} - \frac{1}{i}$, then $ \frac{1}{L} - \frac{1}{\infty} < \sum^{\infty}_{i=L}{ \frac{1}{i^2} }  < \frac{1}{L-1} - \frac{1}{\infty} $.
In fact, we could estimate:
\begin{equation}
  var(\hat{X}^L) = \frac{1}{(L-0.5) \ln^2(2) }
\label{eqn:perf_index_analytic}
\end{equation}
Thus, the Equivalent Number of Look, i.e. L, can be estimated as:
\begin{equation}
\hat{L}_{est} = \frac{1}{var(\hat{X}^L) \ln^2(2)} + 0.5
\label{eqn:enl_analytic}
\end{equation}

@@

\begin{table}
\centering
\begin{tabular}{r|c|c|c|c}
ENL & Var (Theory) & Var (Analysis) & Var (Observed) & $\hat{L}_{est} $ \\
\hline
2  & 1.3423 & 1.3876 & 1.3452 (0.0031) & 2.047 (0.0036)\\
3  & 0.8221 & 0.8326 & 0.8191 (4.2e-5) & 3.041 (0.0001)\\
4  & 0.5907 & 0.5947 & 0.5941 (0.0059) & 4.004 (0.0351)\\
5  & 0.4607 & 0.4625 & 0.4622 (0.0010) & 5.003 (0.0099)\\
6  & 0.3774 & 0.3784 & 0.3800 (0.0009) & 5.977 (0.0131)\\
7  & 0.3196 & 0.3202 & 0.3188 (0.0037) & 7.029 (0.0769)\\
8  & 0.2771 & 0.2775 & 0.2786 (0.0002) & 7.970 (0.0065)\\
9  & 0.2446 & 0.2449 & 0.2455 (0.0007) & 8.979 (0.0244)\\
10 & 0.2189 & 0.2191 & 0.2183 (0.0012) & 10.035 (0.0538)\\
11 & 0.1981 & 0.1982 & 0.1975 (0.0001) & 11.038 (0.0063)\\
12 & 0.1809 & 0.1809 & 0.1810 (0.0022) & 12.001 (0.1419)\\
13 & 0.1664 & 0.1665 & 0.1661 (0.0002) & 13.031 (0.0191)\\
14 & 0.1541 & 0.1542 & 0.1534 (0.0016) & 14.068 (0.1387)\\
15 & 0.1435 & 0.1435 & 0.1432 (0.0019) & 15.036 (0.1967)\\
16 & 0.1342 & 0.1343 & 0.1342 (0.0009) & 16.006 (0.0987)\\
17 & 0.1261 & 0.1261 & 0.1249 (0.0005) & 17.159 (0.0636)\\
18 & 0.1189 & 0.1189 & 0.1192 (0.0010) & 17.959 (0.1406)\\
19 & 0.1125 & 0.1125 & 0.1126 (0.0004) & 18.976 (0.0788)\\
20 & 0.1067 & 0.1067 & 0.1074 (0.0005) & 19.889 (0.0937)\\
21 & 0.1015 & 0.1015 & 0.1017 (0.0002) & 20.975 (0.0357)\\
22 & 0.0968 & 0.0968 & 0.0970 (0.0002) & 21.952 (0.0337)\\
23 & 0.0925 & 0.0925 & 0.0924 (0.0006) & 23.027 (0.1386)\\
24 & 0.0886 & 0.0886 & 0.0887 (0.0002) & 23.957 (0.0507)\\
25 & 0.0849 & 0.0849 & 0.0846 (0.0007) & 25.094 (0.1934)
\end{tabular}
\caption{ Speckle Suppression Power: ENL and Variance }
\label{tab:enl_in_log_domain}
\end{table}

@@

\begin{table}
\centering
\begin{tabular}{c|r|c|c|r}
Pattern  & Filter  & AUC & $MSE_{true}$   & $MSE_{noise}$      \\% &85\%             &90\%\\
\hline
 point  &  unfiltered  &  0.741 (0.7e-3)  &  4.101 (1.3e-3)  &  2e-33 (4e-36) \\
 point  &  pde  &  0.789 (1.3e-3)  &  1.291 (5.1e-3)  &  1.817 (2.2e-3)\\
 point  &  map  &  0.813 (1.4e-3)  &  1.679 (2.2e-3)  &  2.183 (7.4e-3)\\
 point  &  frost  &  0.836 (1.8e-3)  &  0.536 (2.4e-3)  &  4.976 (6.9e-3)\\
 point  &  lee  &  0.857 (0.9e-3)  &  0.615 (3.1e-3)  &  3.189 (0.9e-3)\\
 point  &  boxcar  &  0.871 (1.5e-3)  &  0.471 (1.7e-3)  &  4.503 (5.4e-3)\\
 point  &  kuan  &  0.882 (1.1e-3)  &  0.448 (2.3e-3)  &  3.859 (3.4e-3)\\
\hline
 edge  &  unfiltered  &  0.738 (1.5e-4)  &  4.128 (9.0e-3)  &  2e-33 (1e-35)\\
 edge  &  pde  &  0.783 (0.6e-4)  &  1.409 (0.3e-3)  &  1.589 (0.4e-2)\\
 edge  &  map  &  0.830 (0.6e-4)  &  1.712 (3.5e-3)  &  2.184 (0.8e-2)\\
 edge  &  frost  &  0.841 (0.6e-4)  &  0.551 (0.1e-3)  &  5.035 (1.3e-2)\\
 edge  &  boxcar  &  0.871 (0.2e-4)  &  0.486 (0.2e-3)  &  4.560 (1.3e-2)\\
 edge  &  lee  &  0.872 (0.7e-4)  &  0.619 (2.2e-3)  &  3.233 (1.3e-2)\\
 edge  &  kuan  &  0.885 (0.4e-4)  &  0.471 (2.0e-3)  &  3.909 (1.1e-2)\\
\hline
 checker  &  unfiltered  &  0.738 (4.5e-4)  &  4.11 (7.8e-3)  &  2e-33 (5e-36)\\
 checker  &  pde  &  0.785 (6.2e-4)  &  1.445 (2.6e-3)  &  1.586 (2.4e-3)\\
 checker  &  map  &  0.836 (4.0e-4)  &  1.663 (1.1e-3)  &  2.213 (4.6e-3)\\
 checker  &  frost  &  0.855 (5.6e-4)  &  0.528 (2.2e-3)  &  4.965 (9.3e-3)\\
 checker  &  lee  &  0.879 (2.2e-4)  &  0.605 (1.7e-3)  &  3.229 (2.8e-3)\\
 checker  &  boxcar  &  0.883 (6.4e-4)  &  0.466 (2.4e-3)  &  4.493 (9.1e-3)\\
 checker  &  kuan  &  0.894 (4.2e-4)  &  0.453 (0.9e-3)  &  3.860 (9.5e-3)\\
\hline
 line  &  unfiltered  &  0.737 (1.1e-3)  &  4.129 (7.3e-3)  &  2e-33 (6e-36)\\
 line  &  pde  &  0.752 (1.2e-3)  &  1.339 (2.0e-3)  &  1.885 (3.7e-3)\\
 line  &  map  &  0.801 (1.6e-3)  &  1.706 (5.8e-3)  &  2.188 (3.5e-3)\\
 line  &  frost  &  0.831 (1.3e-3)  &  0.551 (1.1e-3)  &  5.023 (0.5e-3)\\
 line  &  lee  &  0.847 (1.5e-3)  &  0.623 (2.9e-3)  &  3.228 (4.8e-3)\\
 line  &  boxcar  &  0.865 (1.3e-3)  &  0.486 (0.9e-3)  &  4.549 (0.9e-3)\\
 line  &  kuan  &  0.874 (1.9e-3)  &  0.464 (1.9e-3)  &  3.897 (4.9e-3)\\
\hline

@@

\begin{table}
\centering
\begin{tabular}{c|c|c}
Pattern  & AUC - $MSE_{true}$ (p-value) & AUC - $MSE_{benchmark}$ (p-value) \\
\hline
edge & -0.8958 (1.5e-05) &   -0.9778  (1.6e-09) \\
point &     -0.9012   (1.1e-05)   &    -0.9816        (5.3e-10) \\
checker &   -0.9077     (7.3e-06)  &  -0.9829       (3.5e-10) \\
line &      -0.8223     (3.1e-04)  &   -0.9421       (4.8e-07) \\
\hline
\end{tabular}

@@

\begin{figure}
\begin{tabular}{c}
	\subfloat[A Rural Area in Vietnam]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/simulated_images.vietnam_rural.gt.jpg.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[A Suburb of Ha Noi]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/simulated_images.hanoi_suburb.gt.jpg.eps} 	
		 \label{intensity}
	} %\\
%	\subfloat[NTU Campus]{
%		 \epsfxsize=1.5in
%		 \epsfysize=1.5in
%		 \epsffile{src/Aerialcampus.eps} 	
%		 \label{amplitude}
%	} 
%	\hfill	
%	\subfloat[Chu Thap Island of Vietnam]{
%		 \epsfxsize=1.5in
%		 \epsfysize=1.5in
%		 \epsffile{src/fiery.eps} 	
%		 \label{intensity}
%	} 
\end{tabular}
\caption{Ground Truth Images for simulation}
\label{fig:real_simulated_images}
\end{figure}

@@

\begin{table}
\centering
\begin{tabular}{r|r|c|c}
Pattern  & Filter  & $MSE_{true}$   & $MSE_{noise}$      \\% &85\%             &90\%\\
%\hline
%chu thap island	& none		& 4.1066	& 1.2e-33\\
%chu thap island	& pde			& 1.7966	& 1.0866\\
%chu thap island	& lee			& 0.5772	& 3.2378\\
%chu thap island	& frost		& 0.4701	& 4.8608\\
%chu thap island	& kuan		& 0.4196	& 3.7945\\
%chu thap island	& boxcar	& 0.4165	& 4.3952\\
%\hline
%ntu campus	& none		& 4.1231	& 8.7e-35\\
%ntu campus	& pde			& 3.6598	& 0.0733\\
%ntu campus	& lee			& 0.6335	& 3.2673\\
%ntu campus	& frost		& 0.5776	& 5.0569\\
%ntu campus	& boxcar	& 0.5136	& 4.5839\\
%ntu campus	& kuan		& 0.4910	& 3.9444\\
\hline
vietnam rural	& none		& 4.1174	& 3.9e-35\\
vietnam rural	& pde			& 3.8022	& 0.0368\\
vietnam rural	& lee			& 0.4984	& 3.2555\\
vietnam rural	& frost		& 0.3490	& 4.6856\\
vietnam rural	& kuan		& 0.3396	& 3.6877\\
vietnam rural	& boxcar	& 0.3107	& 4.2328\\
\hline
hanoi suburb	& none		& 4.1321	& 4.1e-35\\
hanoi suburb	& pde			& 3.8004	& 0.0391\\
hanoi suburb	& lee			& 0.5261	& 3.2598\\
hanoi suburb	& frost		& 0.3811	& 4.7427\\
hanoi suburb	& kuan		& 0.3619	& 3.7270\\
hanoi suburb	& boxcar	& 0.3395	& 4.2882\\
\hline
\end{tabular}

@@

%\begin{figure*}
\begin{figure}
\normalsize
\begin{center}
\begin{tabular}{c}
	\subfloat[Simulated GrayScale Image (ground-truth)]{
		 \epsfxsize=1.6in
		 \epsfysize=1.6in
		 \epsffile{src/simulated_images.vietnam_rural.gt.jpg.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Unfiltered Image $MSE_{true}=MSE_{base}=4.1174$]{
		 \epsfxsize=1.6in
		 \epsfysize=1.6in
		 \epsffile{src/simulated_images.vietnam_rural.none.fi.jpg.eps} 	
		 \label{intensity}
	} \\
	\subfloat[PDE Result: $MSE_{true}=3.8022,MSE_{noise}=0.0073$]{
		 \epsfxsize=1.6in
		 \epsfysize=1.6in
		 \epsffile{src/simulated_images.vietnam_rural.pde.fi.jpg.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Lee Result: $MSE_{true}=0.4984,MSE_{noise}=3.25553$]{
		 \epsfxsize=1.6in
		 \epsfysize=1.6in
		 \epsffile{src/simulated_images.vietnam_rural.lee.fi.jpg.eps} 	
		 \label{intensity}
	} \\
	\subfloat[Frost Result: $MSE_{true}=0.3490, MSE_{noise} = 4.6856$]{
		 \epsfxsize=1.6in
		 \epsfysize=1.6in
		 \epsffile{src/simulated_images.vietnam_rural.frost.fi.jpg.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Boxcar Result: $MSE_{true} = 0.3107, MSE_{noise}= 4.2328$]{
		 \epsfxsize=1.6in
		 \epsfysize=1.6in
		 \epsffile{src/simulated_images.vietnam_rural.boxcar.fi.jpg.eps} 	
		 \label{intensity}
	}
\end{tabular}

@@

\begin{table}
\centering
\begin{tabular}{c|r|r}
filter & $MSE_{noise}$ & $MSE_{benchmark}$\\
\hline
pde & 0.2583 & 3.8584 \\
map & 2.6936 & 1.4231 \\
kuan & 3.3924 & 0.7243 \\
lee & 3.4172 & 0.6995 \\
boxcar & 3.6918 & 0.4249 \\
frost & 4.1191 & 0.0024 \\
\hline
SLC unfiltered MSE & 4.1167 & 4.1167 
\end{tabular}
\caption{Our Conjecture: Most Suitable Speckle Filter For The Scene Can Be Chosen Using The Residual MSE.}
\label{tab:mse_in_real_image}
\end{table}

%\begin{figure*}
\begin{figure}
\normalsize
\begin{center}
\begin{tabular}{c}
	\subfloat[PDE Filter: $MSE_{benchmark}=3.8584$]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_real.log.image.pde.jpg.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[MAP Filter: $MSE_{benchmark}=1.4231$]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_real.log.image.map.jpg.eps} 	
		 \label{intensity}
	} \\
	\subfloat[Lee Filter: $MSE_{benchmark}=0.6995$]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_real.log.image.lee.jpg.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Frost Filter: $MSE_{benchmark}=0.0024$]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_real.log.image.frost.jpg.eps} 	
		 \label{intensity}
	}
\end{tabular}

\caption{Filtering Real Images: Smaller $MSE_{benchmark}$ suggests visually better images}
\label{fig:real_image_results}
\end{center}
\end{figure}
%\end{figure*}
